Self-reported LLM usage and outcomes on a data science project: Evidence from two undergraduate data science courses

### 2025-04-12 paper/paper.qmd
Added sample sizes to Table 1 (a) and (b)

```{r tbl-year-dist}
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: \"What year are you?\"
#| tbl-subcap: ["STA302 responses (Winter 2024)","STA304 responses (Fall 2024)"]

>>>>

```{r tbl-year-dist}
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: \"What year are you?\"
#| tbl-subcap: ["STA302 responses (Winter 2024); n=92", "STA304 responses (Fall 2024); n=131"]
